\section{Map web service}
\label{sec:call:map}

This section describes the calls required to pull garbage tags and charted areas
out of the system. These are implemented in the
\svnweb{ro/ldir/map/MapWebService}{ro.ldir.map.MapWebService} web resource. The
calls are designed to serve as input for a mapping service, e.g., Google Maps.
Therefore, they output a KML and are performed in anonymous fashion (no
authentication is necessary).

\subsection{Obtaining the garbage tags in a bounding box}

\apilocation{get}{map/ws/garbages/?topLeftX=\param{topLeftX}\&\\topLeftY=\param{topLeftY}\&bottomRightX=\param{bottomRightX}\&bottomRightY=\param{bottomRightY}}
\begin{apidata}{returns}
  \begin{datalist}
    \replyditem{A KML of all the garbages in the bounding box.}
  \end{datalist}
\end{apidata}

\subsection{Obtaining the chart areas intersecting a bounding box}

\apilocation{get}{map/ws/chartedAreas/?topLeftX=\param{topLeftX}\&\\topLeftY=\param{topLeftY}\&bottomRightX=\param{bottomRightX}\&bottomRightY=\param{bottomRightY}}
\begin{apidata}{returns}
  \begin{datalist}
    \replyditem{A KML of all the charted areas intersecting the bounding box.}
  \end{datalist}
\end{apidata}

\subsection{Obtaining the chart areas in a county}

\apilocation{get}{map/ws/countySearch/chartedAreas/\\?county=\param{countyName}}
\begin{apidata}{returns}
  \begin{datalist}
    \replyditem{A KML of all the charted areas in the county.}
  \end{datalist}
\end{apidata}

\subsection{Obtaining the garbage tags in a county}
\apilocation{get}{map/ws/countySearch/garbages/\\?county=\param{countyName}}
\begin{apidata}{returns}
  \begin{datalist}
    \replyditem{A KML of all the garbages in the county.}
  \end{datalist}
\end{apidata}


