\chapter{Calls}
\label{cha:calls}

This chapter describes the calls that the Let's Do It Romania Web Service
accepts. The assumption is that the web service runs on the local machine and it
is accessible at \baselocation. If the web service runs at a different location,
the string ``\baselocation'' must be properly set for each call.

Calls in this section accept take as arguments or return entities described in
Section~\ref{cha:entities} serialized as JSON or XML. The preferred format is
specified in the HTTP headers. For instance, if a client desired the web service
to output format in JSON format during a GET call, the HTTP headers must include
``\texttt{accepts: application/json}''. XML serialization can be obtained by
using the header ``\texttt{accepts: application/xml}''. When an entity is
uploaded to the web service, for instance, through a POST call, the headers to
be used are ``\texttt{content: application/json}'' if the uploaded entity is
provided in JSON format, respectively ``\texttt{content: application/xml}'' when
XML is being employed.

Hereafter, if:
\begin{itemize}
  \item {\sffamily \bfseries method} is a HTTP method such as get, post, put,
    delete, and
  \item \texttt{\param{url}} is the location of a call,
\end{itemize}
then the syntax of a call is represented as:

\bigskip

\apilocation{METHOD}{\param{url}}
\begin{apidata}{content}
  Valid only for put and post requests, describes what kind of data the call
  expects to find embedded in the request.
\end{apidata}
\begin{apidata}{returns}
  Describes a list of possible return values of the call. It can either be an
  entity, a HTTP result code or raw content.
\end{apidata}
\begin{apidata}{access}
  A brief description of who is allowed to make this call.
\end{apidata}

\input{registration}
\input{user}
\input{user_search}
\input{organization}
\input{team}
\input{garbage}
\input{map}
\input{geo}
